### 2022-06-14 chapters/interpretability_background.tex
preliminaries notations updated

The MaxSAT problem is an optimization analog to the SAT problem that finds an optimal assignment satisfying the maximum number of clauses in a CNF. In interpretable machine learning, we consider a \emph{weighted} variant of the MaxSAT problem\textemdash more specifically, a weighted-partial MaxSAT problem\textemdash that optimizes over a set of hard and soft constraints in the form of a weighted-CNF formula. In a weighted-CNF formula, a weight $ {\weight{C_i}} \in \mathbb{R}^+ \cup \{\infty\} $ is defined over each clause $ C_i $, wherein $C_i$ is called a \emph{hard} clause if $\weight{C_i} = \infty$, and  $C_i$ is  a \emph{soft} clause, otherwise.  To avoid notational clutter, we overload {\weight{\cdot}} to denote the weight of an assignment $ \sigma $. In particular, we define $\weight{\sigma}$ as the sum of the weights of \emph{unsatisfied clauses} in a CNF, formally, $$\weight{\sigma} = \sum_{i | \sigma \not \models C_i} \weight{C_i}.$$

Given a weighted-CNF formula $F \triangleq \bigvee_i C_i$ with weight $ \weight{C_i} $, the weighted-partial MaxSAT problems finds an optimal assignment $\sigma^*$ that achieves the minimum weight. Formally,  $\sigma^* = \MaxSAT(F,\weight{\cdot})$ if $\forall \sigma \neq \sigma^*, \weight{\sigma^*} \leq \weight{\sigma}$. The optimal weight of the MaxSAT problem $  \weight{\sigma^*} $ is infinity ($ \infty $) when at least one hard clause becomes unsatisfied.  Therefore,  the weighted-partial MaxSAT problem finds $ \sigma^* $ that satisfies all hard clauses\footnote{In our formulation, we assume that there is a satisfying assignment to a CNF formula containing all hard clauses.} and as many soft clauses as possible such that the total weight of unsatisfied soft clauses is minimum. In Chapter~\ref{chapter:imli}, we reduce the classification problem  to the solution of a weighted-partial MaxSAT problem. The knowledge of the inner workings of {MaxSAT} solvers is  not required for this chapter.

>>>>

The MaxSAT problem is an optimization analog to the SAT problem that finds an optimal assignment satisfying the maximum number of clauses in a CNF. In interpretable machine learning, we consider a \emph{weighted} variant of the MaxSAT problem\textemdash more specifically, a weighted-partial MaxSAT problem\textemdash that optimizes over a set of hard and soft constraints in the form of a weighted-CNF formula. In a weighted-CNF formula, a weight $ {\clauseweight{C_i}} \in \mathbb{R}^+ \cup \{\infty\} $ is defined over each clause $ C_i $, wherein $C_i$ is called a \emph{hard} clause if $\clauseweight{C_i} = \infty$, and  $C_i$ is  a \emph{soft} clause, otherwise.  To avoid notational clutter, we overload {\clauseweight{\cdot}} to denote the weight of an assignment $ \sigma $. In particular, we define $\clauseweight{\sigma}$ as the sum of the weights of \emph{unsatisfied clauses} in a CNF, formally, $$\clauseweight{\sigma} = \sum_{i | \sigma \not \models C_i} \clauseweight{C_i}.$$

Given a weighted-CNF formula $F \triangleq \bigvee_i C_i$ with weight $ \clauseweight{C_i} $, the weighted-partial MaxSAT problems finds an optimal assignment $\sigma^*$ that achieves the minimum weight. Formally,  $\sigma^* = \MaxSAT(F,\clauseweight{\cdot})$ if $\forall \sigma \neq \sigma^*, \clauseweight{\sigma^*} \leq \clauseweight{\sigma}$. The optimal weight of the MaxSAT problem $  \clauseweight{\sigma^*} $ is infinity ($ \infty $) when at least one hard clause becomes unsatisfied.  Therefore,  the weighted-partial MaxSAT problem finds $ \sigma^* $ that satisfies all hard clauses\footnote{In our formulation, we assume that there is a satisfying assignment to a CNF formula containing all hard clauses.} and as many soft clauses as possible such that the total weight of unsatisfied soft clauses is minimum. In Chapter~\ref{chapter:imli}, we reduce the classification problem  to the solution of a weighted-partial MaxSAT problem. The knowledge of the inner workings of {MaxSAT} solvers is  not required for this chapter.
